RNA-seq from 4 cell populations

### 2021-08-03 deconvolution/fans4/molec_profiling.Rmd
bug fix

# set color codes for each cell type
colorCodes = c(
  GABA = '#66A61E',
  GLU = '#E6AB02',
  Olig = '#E7298A',
  MgAs = '#7570B3',
  GABAGLU_vs_Other = '#A6A910',
  GABA_vs_GLU = "grey")

>>>>

# set color codes for each cell type
colorCodes = c(
  GABA = '#66A61E',
  GLU = '#E6AB02',
  Olig = '#E7298A',
  MgAs = '#7570B3')
  # GABAGLU_vs_Other = '#A6A910',
  # GABA_vs_GLU = "grey")
